### 2016-01-28 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
aufgabe 3 a ist fertig

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{caption}
\usepackage{units}
\usepackage{subcaption}

@@

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$ (6)\\\hline
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

@@

\section{Coverage statistics}
\subsection{title}
\subsection{title}
\subsection{title}
\section{Application of the arrival statistic for unitigs}

\section{On distances}
\subsection{title}
\subsection{title}
\begin{thebibliography}{20}

>>>>

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{caption}
\usepackage{units}
\usepackage{subcaption}

@@

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$ (7)\\\hline
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

@@

\section{Theoretical Assignment - \textit{Coverage statistics}}
\subsection{}
\subsection{}
\subsection{}
\section{Theoretical Assignment - \textit{Application of the arrival statistic for unitigs}}

\section{Theoretical Assignment - \textit{On distances}}
\subsection{title}

Consider a tree $T$ constructed with $D$ and the four nodes $i,j,k,l \in T$. Since $D$ is ultrametric, 
the following four inequalities have to hold:
\begin{align}
 d(i,j) &\le max \left\lbrace d(i,k), d(j,k) \right\rbrace \nonumber \\
 d(i,j) &\le max \left\lbrace d(i,l), d(j,l) \right\rbrace \nonumber \\
 d(k,l) &\le max \left\lbrace d(i,k), d(i,l) \right\rbrace \nonumber \\
 d(k,l) &\le max \left\lbrace d(j,k), d(j,l) \right\rbrace \nonumber
\end{align}
W.l.o.g we can assume that $d(i,k) = d(j,k) = d(i,l) = d(j,l)$. With that assumption we can rewrite 
the inequalities as
\begin{align}
 d(i,j) + d(i,j) &\le d(i,k) + d(j,l) \nonumber \\
 d(k,l) + d(k,l) &\le d(i,l) + d(j,k) \nonumber
\end{align}
And also the following inequality is valid:
\begin{equation}
 d(i,j) + d(k,l) \le max \left\lbrace d(i,k) + d(j,l), d(i,l) + d(j,k) \right\rbrace \nonumber
\end{equation}
As one can see, that is the Four-Point-Condition (4PC) and a metric fulfill 4PC if and only if it is 
additive. So $D$ is a tree metric $\square$

To show the back direction one consider the four elements $A, B, C, D \in X$ of a taxa $X$ and the 
following distance matrix:
\begin{equation}
 D = \begin{bmatrix}
        & B & C & D \\
      A & 7 & 6 & 5 \\
      B &   & 3 & 6 \\
      C &   &   & 5
     \end{bmatrix} \nonumber
\end{equation}
One can see in the script of this lecture that $D$ is a tree metric. But the Three-Point-Condition 
(3PC) is not fulfilled as can be easily shown. To fulfill 3PC the following inequality has to be 
valid:
\begin{equation}
 d(A,B) \le max \left\lbrace d(A,C), d(B,C) \right\rbrace \nonumber
\end{equation}
but
\begin{equation}
 7 \nleq max \left\lbrace 6, 3  \right\rbrace \nonumber
\end{equation}
So $D$ does not fulfill 3PC and thus $D$ is not ultra metric. $\square$

\subsection{}

\begin{thebibliography}{20}
